\chapter*{Abstract}

This scientific project work deals with the evaluation of Frameworks for hybrid and cross-platform application development. First of all some already published work is being analysed. After that an explanation of the concepts of hybrid and cross-platform development is given and the platforms that are relevant for this work are presented. Additionally an introduction to the functionality of the sensors which usage is being tested in this work is given. After that the requirement analysis follows with its functional and not-functional conditions for the evaluation.
\\
\\
In the following market analysis the 3 actual most relevant Frameworks for hybrid and cross-platform application development are determined. Those are presented afterwards. Subsequently the procedure to specificate the evaluation criteria is declared an the criteria are explained one for one. 
\\
\\
After the declaration of the evaluation criteria the planning of the functions-test-application follows. With help of this application the 3 chosen Frameworks are tested in terms of the usage of various functions. Furthermore this application is defined and presented in an object-oriented analysis and design with the appropriate UML diagrams. After that the implementation of the functions-test-application with the 3 chosen frameworks is introduced. In the following evaluation the 3 chosen Framework are analysed according to the above mentioned evaluation criteria. Base of this evaluation are the implementation and further research concerning the 3 chosen frameworks. 
\\
\\
At the end a concluding comparison of the evaluated frameworks and a recommendation is given. This is followed by a forecast for further work. 